%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
  % Awesome CV LaTeX Template for Cover Letter
  %
  % This template has been downloaded from:
  % https://github.com/posquit0/Awesome-CV
  %
  % Authors:
  % Claud D. Park <posquit0.bj@gmail.com>
  % Lars Richter <mail@ayeks.de>
  %
  % Template license:
  % CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
  %


% CONFIGS ------------------------------------------------------------------------------
  \documentclass[11pt, letterpaper]{awesome-cv} % 'letterpaper' or 'a4paper'
  \geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm} % page marg
  \include{config/colors.tex}
  \renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % set social delim as pipe
  \input{config/personal-info.tex}

%	LETTER INFO - All required ---------------------------------------------------------
  \recipient % The company being applied to
    {UCSF}
    {400 Parnassus Ave\\San Francisco, CA 94143, }
  % The date on the letter, default is the date of compilation
  \letterdate{\today}
  % The title of the letter
  \lettertitle{Job Application for Computational and Data Science Research 3 position}
  % How the letter is opened
  \letteropening{\\Dear Hiring Team,}
  % How the letter is closed
  \letterclosing{Sincerely,}
  % Any enclosures with the letter
  \letterenclosure[Attached]{Résumé}
% DOC BODY -----------------------------------------------------------------------------
\begin{document}
\makecvheader[C] % Print the header with above info, optional alignment (L,R,C)
\makecvfooter {}{Chris Brozdowski~~~·~~~Cover Letter}{} % 3 arg(left, center, right)
\linebreak
\makelettertitle % Print the title with above letter information
%	LETTER CONTENT
\begin{cvletter}
  \lettersection{About Me}
  I am excited to apply for the Computational and Data Science Research 3 position at the University of California San Francisco and eager to join the Frank Laboratory to work on their Spyglass pipeline. As a highly skilled data scientist with a deep understanding of neuroscience, Python, git, and DataJoint, I believe I would be a valuable addition to the team.
  \lettersection{Why UCSF?}
  I am particularly drawn to the Frank Laboratory and UCSF due to their reputation for cutting-edge research and innovation. The Frank Lab has a long-standing history of developing pioneering methods for studying neural circuits and their contributions to behavior. The lab's focus on computational and data-driven approaches to neuroscience research aligns perfectly with my own passion for leveraging technologies to support research.
  \lettersection{Why Me?}
  I have extensive experience in data analysis, visualization, pipeline design, and research software integration. As a former DataJoint employee, I have expertise in the foundational technologies that support the Spyglass pipeline, making me an ideal candidate for this role. I have contributed to both the DataJoint Python API and various complimentary DataJoint products. I have a deep understanding of DataJoint's capabilities and limitations, and I am confident that I can leverage this knowledge to support and optimize ongoing work.\par
  Furthermore, I have a strong track record of communicating complex concepts, including principles of pipeline design and software engineering, to multidisciplinary scientific teams. I have successfully led research projects involving large datasets and complex analyses. I have also published several papers in peer-reviewed journals, showcasing my deep understanding of the scientific process.\par
  I am excited about the opportunity to join the Frank Laboratory at the University of California San Francisco and contribute to cutting-edge research in neuroscience. Thank you for considering my application.
% \lettersection{Why Atomwise?}
% \input{cover/about-me.tex}
% \input{cover/why-you.tex}
% \input{cover/why-me.tex}
\end{cvletter}
\makeletterclosing % Print the signature and enclosures
% Now randomly selects across images/sigX.png where X is 1,2,3 to print signature image
\end{document}

