%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\iffalse % comment wrapper til \fi
  \cventry % Template
    {Job title}
    {Organization}
    {Location}
    {YEAR - YEAR}
    {
      \begin{cvitems}
        % Accomplished X as measured by Y, by doing Z
        \item {Description(s) of tasks/responsibilities}
      \end{cvitems}
    }
\fi

%---------------------------------------------------------
  \cventry
    {Director of Customer Development (Remote, part-time)}
    {Censibal}
    {Houston, TX}
    {02/23/2023 - Present}
    {
      \begin{cvitems}
        \item { Developed community relationships and partnerships to increase
          brand awareness and steer product development.}
        \item { Drove implementation of online presence and marketing strategies
          to increase customer acquisition and brand awareness.}
      \end{cvitems}
    }
%---------------------------------------------------------
\vspace{\baselineskip}
  \cventry
    {Computational and Data Science Research Specialist III (Remote)}
    {University of California, San Francisco}
    {San Francisco, CA}
    {05/22/2023 - Present}
    {
      \begin{cvitems}
        \item {Lead development of Spyglass, a data management, analysis, and
          visualization platform, to improve research efficiency and reproducibility.}
        \item {Introduced professional software management strategies to shared data
          infrastructure to improve efficiency and add features to underlying
          framework, including selective SQL database export, pipeline
          versioning mechanisms, and centralizing code with class inheritance.}
        \item {Coordinated with outside stakeholders to develop a cloud-based
          demonstration of the pipeline to improve user experience and adoption.}
        \item {Hosted regular workshops to train lab members in software- and
          pipeline-development, improving productivity and code maintainability.}
      \end{cvitems}
    }
%---------------------------------------------------------
\vspace{\baselineskip}
  \cventry
    {Neuroscience Data Engineer II}
    {DataJoint}
    {Houston, TX}
    {10/18/2021 - 02/23/2023}
    {
      \begin{cvitems}
        \item {Developed data management, analysis, and visualization pipelines
          using Python, GitHub, MySQL, Docker, and plotly for multi-site
          neurobiology research to improve efficiency through RDS automation.
          Led development of a pipeline for managing ML/AI pose-estimation models.}
        \item {Worked with clients to build custom data infrastructure, including
          API import/export tools, to automate pipelines deployed in AWS cloud.}
        \item {Parameterized pytest integration testing, and developed mkdocs
          documentation using gh-actions to improve open-source contributor experience.}
        % \item {Led the development of communication strategies for YouTube
        %   content and conference sales-lead cultivation.}
        \item {Conducted UX interviews to improve tool utility and leveraged
          interview format into into social media content to promote product offerings.}
        \item {Developed company graphic design assets using Adobe Suite to
          improve brand cohesion across social media, documentation, and presentations.}
        % \item {Reformed internal Slack communication standards and GitHub project management practices to promote cross-team collaboration and efficiency.}
        % \item {Developed relationships with software and data standards developers in the field to grow partnerships and mutual sustainability commitments.}
      \end{cvitems}
    }
%---------------------------------------------------------
\vspace{\baselineskip}
  \cventry
    {Postdoctoral Researcher}
    {Brain Development Lab, Vanderbilt University}
    {Nashville, TN}
    {10/01/2019 - 10/01/2021}
    {
      \begin{cvitems}
        \item{Implemented data collection/management procedures with shell and
          Excel validation tools to ensure fitness for analysis.}
        \item{Evaluated scientific evidence regarding various language and
          cognition measures to support data collection for a 5-year R01 study.}
        \item{Generated/refined analytical/quantiative models of datasets using
          shell, MATLAB, and R. Published written summaries of analyses.}
        \item{Mentored undergraduate and masters students in the development of
          key research skills, including data integrity and standardization best practices.}
      \end{cvitems}
    }
%---------------------------------------------------------
\vspace{\baselineskip}
  \cventry
    {Postdoctoral Researcher}
    {Cognitive Semiotics Lab, RWTH Aachen University}
    {Aachen, Germany}
    {10/15/2018 - 10/01/2019}
    {
      \begin{cvitems}
        \item{Developed novel experiments using motion capture technology and
          MATLAB to explore qualitative and quantiative trends.}
        \item{Implemented data collection for research, establishing norms and
          documentation for subsequent projects.}
        \item{Collaborated with acoustics and virtual reality teams to contribute
          to the scientific literature on naturalism-perception effects in virtual reality.}
        \item{Taught and co-taught undergraduate and masters courses related to
          statistics, psychology, and linguistics across local and partner universities.}
      \end{cvitems}
    }
%---------------------------------------------------------
\vspace{\baselineskip}
  \cventry
    {Graduate Researcher}
    {Laboratory for Language and Cognitive Neuroscience, San Diego State University}
    {San Diego, CA}
    {08/15/2013 - 08/15/2018}
    {
      \begin{cvitems}
        \item {Adapted psycholinguistic behavioral and fMRI paradigms for sign
          language research, including spatial cognition, co-thought gesture,
          and motor simulation. Organized and analyzed resulting data with shell,
          Excel, R, ANCOVA, and linear mixed-effects models to contribute to
          scientific literature.}
        \item {Automated key aspects of experimental design,
          % including randomization, stimulus presentation, and publication formatting,
          using shell, Python, ffmpeg, and \LaTeX, improving iteration
          cycles and reducing human error.}
        % \item{Managed multiple project schedules via task trackers and
        %   mentored research assistants
        %   in statistical methods, transcription, and research tools.}
        % \item {Shared scientific findings via conference posters, verbal presentations and manuscripts for peer-reviewed publications.}
      \end{cvitems}
    }
%---------------------------------------------------------
% \vspace{\baselineskip}
%   \cventry
%     {Research Assistant}
%     {\textit{Various Labs}, University of Connecticut}
%     {Storrs, CT}
%     {2010 - 2013}
%     {
%       \begin{cvitems}
%         \item {Led grant-funded projects on (a) eye-tracking as a measurement of semantic network models and (b) verb use among language-deprived signers.}
%         % \item {Assisted in (a) EEG research on syntax and (b) linguistics research on ASL phonology.}
%       \end{cvitems}
%     }

%---------------------------------------------------------
\end{cventries}
