%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
% \cvsection{Selected Academic publications}
\cvsection{Academic publications}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\cvsubsection{Manuscripts}\par
%---------------------------------------------------------
\begin{cvparagraphlist}
  Emmorey, K., \textbf{Brozdowski, C.}, \& McCullough, S. (2021). The neural correlates for spatial language: Perspective-dependent and -independent relationships in American Sign Language and spoken English, \textit{Brain and Language}, 223, 105044. \par 
  \textbf{Brozdowski, C.} \& Booth, J.R. (2021) Reading skill correlates in frontal cortex during semantic and phonological processing. \textit{PsyArXiv}. \par 
  \textbf{Brozdowski, C.}, Secora, K., \& Emmorey, K. (2019). Assessing the Comprehension of Spatial Perspectives in ASL Classifier Constructions. \textit{The Journal of Deaf Studies and Deaf Education} 24(3), 214-222. \par 
  \textbf{Brozdowski, C.} \& Emmorey, K. (2020) Shadowing in the manual modality. \textit{Acta Psychologica}, 108, 103092. \par 
\end{cvparagraphlist}

%---------------------------------------------------------
\cvsubsection{Presentations}\par
%---------------------------------------------------------
\begin{cvparagraphlist}
  \textbf{Brozdowski, C.}, Gunalan, K., Nguyen, T., Dincer, T., \& Yatsenko, D. (2022). Automated Research Workflows for Pose Estimation, Neuromatch Academy, Virtual. \par
  Gunalan, K., \textbf{Brozdowski, C.}, Nguyen, T., Dichter, B., Ruebel, O., Ly, R., \& Yatsenko, D. (2022). Automated analysis and sharing of neuroscience data using DataJoint, Neurodata Without Borders, and DANDI. 8th Annual BRAIN Initiative Meeting, Virtual. \par
  Dincer, T., Nguyen, T., Gunalan, K., \textbf{Brozdowski, C.}, \& Yatsenko, D. (2022) A Complete Data Pipeline for Calcium Imaging in DataJoint. INCF Assembly, Virtual. \par
  Kartheiser, G., Kurz, K., Emmorey, K., \textbf{Brozdowski, C.}, \& Hauser, P. (2022). Learning Sign Language as a Second Language Facilitates Nonlinguistic Spatial Cognitive Skills. International Conference on Sign Language Acquisition, Virtual. \par
  \textbf{Brozdowski, C.}, Scruggs, A., Quinto-Pozos, D., Schuele, M., \& Booth, J.R. (2020; canceled). Mapping reading networks in deaf \& hearing children considering language modality. Society for the Scientific Study of Reading, Long Beach, California. \par
  Ehret, J., Stienen, J., \textbf{Brozdowski, C.}, et al. (2020) Evaluating the Influence of Phoneme-Dependent Dynamic Speaker Directivity of Embodied Conversational Agents' Speech. Paper presented at ACM International Conference on Intelligent Virtual Agents, Glasgow, United Kingdom. \par
  \textbf{Brozdowski, C.}, \& Emmorey, K. (2019). Using transitional information in sign and gesture prediction. Poster presented at Theoretical Issues in Sign Language Research, Hamburg, Germany. \par
  \textbf{Brozdowski, C.}, Tewari, A., \& Mittelberg, I. (2019). Purposeful and Transitional Velocity among Sign Language Users: A Motion Capture Study. Poster presented at LingCologne2019: Multimodality, Cologne, Germany. \par
  McCullough, S., \textbf{Brozdowski, C.}, \& Emmorey, K. (2019, March). Neural correlates for comprehending perspective-independent and perspective-dependent spatial expressions in ASL and English. Poster presented at the Cognitive Neuroscience Society, San Francisco. \par
  \textbf{Brozdowski, C.}, \& Emmorey, K. (2018, July). Shadowing linguistic and non-linguistic body movements. Paper presented at the International Society for Gesture Studies, Cape Town, South Africa. \par
  \textbf{Brozdowski, C.}, Emmorey, K. (2016). Co-Thought Gesture in Bimodal Bilinguals. Poster presented at the 12th Conference on Theoretical Issues in Sign Language Research. Melbourne, Australia. \par
  \textbf{Brozdowski, C.}, Gordils, J., Magnuson, J. (2013). Contra the Qualitatively Different Representation Hypothesis (QDRH), Concrete Concepts Activate Associates Faster than Abstract Concepts. Paper presented at the Annual Meeting of the Psychonomic Society, Toronto, Canada. \par
  \textbf{Brozdowski, C.}, Gordils, J., Magnuson, J. (2013). Using Text Instead of Pictures in the Visual World Paradigm: Phonological, Semantic, and Perceptual Similarity Effects. Poster presented at the Annual Meeting of the Psychonomic Society, Toronto, Canada.  \par
\end{cvparagraphlist}